---
title: "game analytics"
author: 
date: "10/16/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This project is about clustering and the goal is including video game analytics as part of their sports consulting practice group. The data scraped is about the game "player unknown's Battlegrounds".

## Preparation
```{r}
library(tidyverse)
library(fclust)
library(NbClust)
library(mclust)
library(cluster)
library(factoextra)

## load the data
player_stats <- read_csv("BDS_WK08_PUBG_Player_Statistics-1.csv")
player_stats %>% head()
str(player_stats)

```

```{r}
## subsetting the data
solo_players <- player_stats %>% select(contains("solo_"))
solo_players %>% names()
```

## Data Preparation
```{r}
## remove all the missing values if any
solo_players <- na.omit(solo_players)
## scale the data
solo2 <- data.frame(apply(solo_players,2,scale))
colnames(solo2) <- colnames(solo_players)


## scaling introduced some NAs so we can remove the columns with nas
solo2 <- solo2 %>% select(-c(solo_Revives,solo_RevivesPg,solo_WeaponAcquired,solo_DBNOs))

## sample the data
set.seed(123)
solo3 <- solo2 %>% sample_frac(0.15, replace = FALSE)
```


## K-means
```{r}
## getting the distances
distance <- get_dist(solo3)

## kmeans
k2 <- kmeans(solo3, centers = 2)
k2
```

```{r}
clusplot(solo3, k2$cluster)
```

```{r}
## tuning the kmeans
k3 <- kmeans(solo3, 3, nstart = 25, iter.max = 50)

## plotting
clusplot(solo3, k3$cluster)
```


```{r}
fviz_cluster(k3, data = solo3)
```



 ## Summary of the results
using 3 as our number of clusters we can perform the final analysis and extract the results using 3 clusters.
```{r}
## fitting the final model
final <- kmeans(solo3, 4, nstart = 25, iter.max = 30)
final
```
```{r}
## visualizing we get
fviz_cluster(final,data = solo3)
```

Now we can extract the clusters and add to the initial data to do some descriptve statiatcs at the cluster level.
```{r}
## initial datas duplicate
set.seed(456)
sol3_dup <- solo_players %>% sample_frac(0.15, replace = FALSE)

sol3_dup %>% mutate(Cluster = final$cluster) %>% 
  group_by(Cluster) %>% 
  summarise_all("mean")
```

From the model we got 4 optimal clusters, and after doing some summary statistics we can say the quality was good. having a withinness of 35% that is the quality of partition, had no real interpretation as we know the higher percentage means a better partition. 